Detecting changes in dispersion in COVID-19 incidence time series using a negative binomial model

### 2025-01-14 manuscript/ms (2).tex
Improve data availability statement
Update figure captions

COVID-19 cumulative case data are from [The New York Times](https://github.com/nytimes/covid-19-data/) and county population sizes are from [The United States Census Bureau](https://www2.census.gov/programs-surveys/popest/datasets/2020-2021/counties/totals/. Cumulative cases for the largest three counties in each state were converted to weekly counts by keeping the last observation from each week and differenced to compute new cases.

@@

\begin{figure}[!h]
\includegraphics[width=1\textwidth]{fig1}
\caption{
Detecting dispersion changes in incidence time series in populations of different sizes. a: Simulated case counts when dispersion is constant. b: Simulated case counts when dispersion changes. c: Constant dispersion parameter used in generation of the above. d: Changing dispersion parameter used in generation of the above. e, f: Performance of the LRT with simulated data that have different absolute differences in \begin{math}\theta\end{math} (horizontal axis of each panel) illustrates p-value distribution in population size of 50,000 (e) and population size of 10,000,000 (f), which represent the range in the empirical data. O and X mark the null and alternative hypotheses indicated in panels c and d. Red vertical lines represent the interquartile range. 
 }
\label{fig1}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.85\textwidth]{fig3.pdf}
\caption{
Incidence and dispersion between 2020-01-04 and 2023-03-18 in large counties in the US. a: Mean COVID-19 cases of the 144 US counties over time. b: Mean $\theta$ of the 144 US counties over time. c: log10(case counts) - log10(reporting rate) over time for each of the large counties (y-axis). This represents $log_{10}\theta$ under the model in Equation 1. d: $log_{10}\theta$ over time for each of the large counties (y-axis). e: Binned $log_{10}\theta$ estimates for all counties over time. f: LRT p-values over time for each of the large counties (y-axis).
}
\label{fig3}
\end{figure}

>>>>

COVID-19 cumulative case data are from [The New York Times](https://github.com/nytimes/covid-19-data/) and county population sizes are from [The United States Census Bureau](https://www2.census.gov/programs-surveys/popest/datasets/2020-2021/counties/totals/. Cumulative cases for the largest three counties in each state were converted to weekly counts by keeping the last observation from each week and differenced to compute new cases. Note that missing values for new cases were all at the beginning of the pandemic and were imputed as zero. Apprxoimately 0.24% of new cases were negative due to corrections in the cumulative data. These were also imputed as zero.

@@

\begin{figure}[!h]
\includegraphics[width=1\textwidth]{fig1}
\caption{
Detecting dispersion changes in case count time series. a: Sampled time period (red line) from overall US COVID-19 incidence per 1,000 people between 2020-01-04 and 2023-03-18. b: Cases per 1,000 people in Douglas County, NE over the sample time period with estimated mean values (red) and estimated dispersion values on either side of the midpoint. c: Estimated $\theta$ v. true $\theta$  with values outside of tolerance plotted in purple (close to Poisson) and blue (close to collapsing to zero). d: p-value versus absolute difference in $log_{10}\theta$. Red curve and red shading depict ***, respectively. 
 }
\label{fig1}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.85\textwidth]{fig3.pdf}
\caption{
Incidence and dispersion between 2020-01-04 and 2023-03-18 in large counties in the US. a: Mean COVID-19 cases of the 144 US counties over time. b: Mean $log_{10}\theta$ of the 144 US counties over time. Dashed line represents expected value of $log_{10}\theta_0$ under the null model in Equation 1. c: log10(case counts) - log10(reporting rate) over time for each of the large counties (y-axis). This again represents $log_{10}\theta_0$ under the model in Equation 1. d: $log_{10}\theta$ over time for each of the large counties (y-axis). e: Binned $log_{10}\theta_0$ for all counties over time. f: LRT p-values over time for each of the large counties (y-axis).
}
\label{fig3}
\end{figure}
